### 2017-05-31 paper.tex
Editing

\fixme{65}{Write conclusion}

>>>>

Every day,
teachers all over the world spend countless hours duplicating each other's work.
These ten rules provide an alternative:
adopting the model of collaborative software development
to make more robust and sustainable lessons
that can be continually improved by those who use them.
We hope that our experiences can help others teach more
with more impact and less effort.
